### 2021-07-04 rad-icfp-2021/purerad.tex
adding example

\begin{example}
    The reverse-mode transformation of the terms from the introduction is

    \begin{tabular}{c r}
        &$\directD{\rho}{\Gamma}{Y}$(!let w1 = x1 * x2 in let w2 = w1 * x1 in w2!) \\
        =& TODO \\
        \\
        $\directD{\rho}{\Gamma}{Y}$(!prod(A)!) \\
        =& \\
        % !dot(A,B)!
    \end{tabular}
\end{example}

@@

    \begin{tabular}{c r}
        & $\grad_\Gamma$(!let w1 = x1 * x2 in let w2 = w1 * x1 in w2!) \\
        =& TODO \\
        \\
        $\grad_\Gamma$(!prod(A)!) \\
        =& \\
        % !dot(A,B)!
    \end{tabular}
\end{example}

>>>>

\begin{example}
    The reverse-mode transformation of the terms from the introduction are given by

    \begin{tabular}{c l}
        &$\directD{\rho}{\Gamma}{Y}$(!let w1 = x1 * x2 in let w2 = w1 * x1 in w2!) \\
        =& !let w1,Y1=!\\
        & \quad\quad !let y11,Y11= <x1, fun (y1,y2,y3,z) -> Y(y1+z,y2,y3)> in! \\
        & \quad\quad !let y12,Y12= <x2, fun (y1,y2,y3,y4,z) -> Y11(y1,y2+z,y3,y4)> in! \\
        & \quad\quad !<y11 * y12, fun (y1,y2,y3,z) -> Y12(y1,y2,y3,y12*z,y11*z) > in! \\
        & !let w2,Y2=!\\
        & \quad\quad !let y21,Y21= <w1, fun (y1,y2,y3,y4,z) -> Y(y1,y2,y3,y4+z)> in! \\
        & \quad\quad !let y22,Y22= <x1, fun (y1,y2,y3,y4,y5,z) -> Y11(y1+z,y2,y3,y4,y5)> in! \\
        & \quad\quad !<y21 * y22, fun (y1,y2,y3,y4,z) -> Y22(y1,y2,y3,y4,y22*z,y21*z) > in! \\
        & !let y,Y3= <w, fun (y1,y2,y3,y4,z) -> Y2(y1,y2,y3,y4+z)> in! \\
        & !<y, fun (y1,y2,y3,z) -> Y3(y1,y2,y3,0,z) >!
    \end{tabular}
    \medskip

    \begin{tabular}{c l}
        &$\directD{\rho}{\Gamma}{Y}$(!prod(A)!) \\
        =& !let x,Y1= <0, fun (X,z) -> Y(X)> in! \\
        & !let B,Y2= <A, fun (X,x,Z) -> Y(X+Z,x)> in!\\
        & !let A0= scanl * x B in!\\
        & !let A1= map2 (a,b.b) A0 B in!\\
        & !let A2= shift1 (map2 (a,b.a) A0 B) in!\\
        & !let A3= scanr * 1 A1 in!\\
        & !<prod(B), fun (X,z) -> Y2(X,0,map2 (a,b. a*z*b) A2 A3)>! 
    \end{tabular}
\end{example}

@@

    \begin{tabular}{c r}
        & $\grad_\Gamma$(!let w1 = x1 * x2 in let w2 = w1 * x1 in w2!) \\
        =& TODO \\
        \\
        $\grad_\Gamma$(!prod(A)!) \\
        =& \\
    \end{tabular}
\end{example}
